%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.3, 30 April 2017) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=0.5cm,right=7cm,marginparwidth=6cm,marginparsep=0.5cm,top=0.5cm,bottom=0.5cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Black}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{greencustom}{HTML}{45540E}
\colorlet{heading}{greencustom}
\colorlet{accent}{Black}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Brendon A. Kay}
\tagline{Data Engineering - Systems Software Development}
%% \photo{2.8cm}{Globe_High}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:bak04280@gmail.com}{bak04280@gmail.com}}
  \location{Golden, CO, USA}
  \homepage{\href{https://brendonakay.github.io}{brendonakay.github.io}}
  \linkedin{\href{https://www.linkedin.com/in/brendon-kay-39298366}{brendon-kay-39298366}}
  \github{\href{https://github.com/brendonakay/}{brendonakay}}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Technical Operations Lead Developer}{Maize Analytics}{June 2020 -- Present}{Remote}
Managed scrum backlog and project priorities. Advised on overall project architecture. 
Helped Junior developers in pair programming sessions.

\divider

\cvevent{Technical Operations Developer}{Maize Analytics}{January 2019 -- June 2020}{Remote}
Developed integration and ETL tools for the business applications. 
Maintained VMs and containers of various software services. Maintained AWS cloud infrastructure.

\divider

\cvevent{Data Analyst}{Vail Resorts}{September 2018 -- January 2019}{Broomfield, CO}
Extract information for ad campaigns and for the Data Science and Governance team.
Wrote ETL scripts using SQL and Python. Contracted pm a per-quarter basis.

\divider

\cvevent{Application Support Engineer}{Logic Supply, Inc.}{November 2017 -- September 2018}{South Burlington, VT}
Develop internal tooling to support the production systems of the org's ERP and website. 
Implemented in-house auditing tools for analytics and fault prevention. Maintained 
Google business tools, such as Google Scripts, for business intelligence reporting.

\divider

\cvevent{QA Engineer}{Logic Supply, Inc.}{April 2017 -- November 2017}{South Burlington, VT}
Quality assurance of the org’s e-commerce website and ERP system through
manual testing methods, user acceptance testing, and by reviewing and developing unit 
tests. Maintained and developed the GitLab CI for automated and scheduled test 
runs and code quality checks. Wrote automated functional tests in Selenium and 
Python for automated website testing.

\divider

\cvevent{QA Engineer}{Allscripts Healtchare Solutions, Inc.}{September 2016 -- March 2017}{South Burlington, VT}
Quality assurance of the TouchWorks EMR product by means of automated testing.
Developed Selenium scripts, coordinating user acceptance testing, and research 
requirements for products and solutions.
\divider

\cvevent{Support Engineer}{Union Street Media}{February 2015 -- March 2016}{Burlington, VT}
LAMP stack web development. Daily activities included writing backend PHP code, 
configuring DNS for a client, as well as maintaining the MySQL databases.

%\cvsection{Projects}

%\cvevent{Real-time EMR message processing tool}{Code is proprietary. Please email me for further details.}
%A Hyperledger Composer business network that functions as a transparent and immutable Supply Chain
%ecosystem for manufacturing computers using open source blockchain technology:
%\smallskip
%\begin{itemize}
%\item Go
%\item Software architecture
%\item Microservices
%\end{itemize}
%
%\medskip

% \cvsection{A Day of My Life}
% 
% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% \wheelchart{1.5cm}{0.5cm}{%
%   3/6em/accent!30/Sports \& Hobbies,
%   8/8em/accent!80/Work,
%   1/8em/accent!10/Transport,
%   2/10em/accent!20/Personal IT projects,
%   8/8em/accent!80/Sleep,
%   2/6em/accent!20/Cooking \& Eating
% }

%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the 
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}
